### 2017-03-12 README.Rmd
added subdirectorytools

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

@@

As a first example, we'll fit a random forest to the famous Boston housing data included with the package (see `?boston` for details). In fact the original motivation for this package was to be able to compute two-predictor partial dependence plots from random forest models in R. 
```{r, fig.width=8, fig.height=4, message=FALSE}
# Fit a random forest to the Boston housing data
library(randomForest)  # install.packages("randomForest")
data (boston)  # load the boston housing data
set.seed(101)  # for reproducibility
boston.rf <- randomForest(cmedv ~ ., data = boston)

@@

```{r, fig.width=8, fig.height=4, message=FALSE}
# Fit an SVM to the Pima Indians diabetes data
library(kernlab)  # install.packages("kernlab")
data (pima)  # load the Pima Indians diabetes data
pima.svm <- ksvm(diabetes ~ ., data = pima, type = "C-svc", kernel = "rbfdot",
                 C = 0.5, prob.model = TRUE)

>>>>

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "tools/README-"
)
```

@@

As a first example, we'll fit a random forest to the famous Boston housing data included with the package (see `?boston` for details). In fact the original motivation for this package was to be able to compute two-predictor partial dependence plots from random forest models in R. 
```{r example-rf, fig.width=8, fig.height=4, message=FALSE}
# Fit a random forest to the Boston housing data
library(randomForest)  # install.packages("randomForest")
data (boston)  # load the boston housing data
set.seed(101)  # for reproducibility
boston.rf <- randomForest(cmedv ~ ., data = boston)

@@

```{r example-svm, fig.width=8, fig.height=4, message=FALSE}
# Fit an SVM to the Pima Indians diabetes data
library(kernlab)  # install.packages("kernlab")
data (pima)  # load the Pima Indians diabetes data
pima.svm <- ksvm(diabetes ~ ., data = pima, type = "C-svc", kernel = "rbfdot",
                 C = 0.5, prob.model = TRUE)
